Crowdy: Social Crowd Visualization

### 2011-03-01 docs/crowdy_gui.tex
added implementation

In the other study based on the previous one, K. Y. Kamath et
al\cite{kamath2011transient}, they add another salient feature - a novel crowd
tracking and evolution approach for linking crowds across time periods. Unlike
the more static and long-lived group-based membership offered on many social
networks their goal is to support the discovery of organic and highly-temporal
group affiliation, which they refer to as ``transient crowds''. A transient
crowd according to them is a potentially short-lived ad-hoc collection of users
bound together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in “Crowdy” in a
similar fashion.

@@

\section{Implementation}
The system is designed to run in a user's web browser.
As a result, we choose to use some fairly standard web tools to implement the system.
The system that we are building the user interface on top of exposes a RESTful API.
To retrieve data, our system makes an HTTP GET request to the server.
The server returns data in the JSON format, which is easy to decode in Javascript.

CherryPy
Jinja

jQuery
Simile Timeline
Google Maps API

>>>>

In the other study based on the previous one, K. Y. Kamath et
al\cite{kamath2011transient}, they add another salient feature - a novel crowd
tracking and evolution approach for linking crowds across time periods. Unlike
the more static and long-lived group-based membership offered on many social
networks their goal is to support the discovery of organic and highly-temporal
group affiliation, which they refer to as ``transient crowds''. A transient
crowd according to them is a potentially short-lived ad-hoc collection of users
bound together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in ``Crowdy'' in a
similar fashion.

@@

\section{Implementation}
The system is designed to run in a user's web browser.  As a result, we decided
to use some fairly standard web tools to implement the system.  The system that
we are building the user interface on top of exposes a RESTful API.  To
retrieve data, our system makes an HTTP GET request to the server.  The server
returns data in the JSON format, which is easy to decode in Javascript.

We are writing the portion of the web application that runs on the server in
python, since that is what our team has the most experience with.  We chose the
CherryPy framework to build the application because it is simple and lets us
write testable code.  We are using the Jinja templating engine to generate the
HTML pages.

The code that will run on the user's web browser has to be written in
Javascript.  We use the jQuery library to handle events, retrieve JSON, and
abstract away the idiosyncrasies of the various web browsers.  We are using the
Simile Timeline library to produce the crowd timelines.  In the future, we may
use the Google Maps API to display crowds on a map.
